Lipid Interactome Monthly Invoice

### 2025-09-04 HourlyTracking/202508_GG-Hours.qmd
updated hours page, saved copy of letter to editor

---
title: August 2025 Lipid Interactome Monthly Invoice
author: "Gaelen Guzman"
date: "2025 09 04"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 09 04}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

@@

Please find below the hours I logged for the month of August 2025, with descriptions of each day's activity. In total, I performed 4 hours of work at an hourly rate of $50 (USD), for a total bill of $200.

>>>>

---
title: Lipid Interactome Monthly Invoice
subtitle: August 2025
author: "Gaelen Guzman"
date: "2025 09 04"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 09 04}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

@@

Please find below the hours I logged for the month of August 2025, with descriptions of each day's activity. In total, I performed 5 hours of work at an hourly rate of $50 (USD), for a total bill of $250.
